European or American? A re-examination of the transatlantic influence over the IMF

### 2025-04-22 demo/demo.qmd
Fix yaml

---
title: European or American? A re-examination of the transatlantic influence over the IMF
# subtitle: GV499 Dissertation
header-includes: |
  \AtBeginDocument{\title[GV499 Dissertation]{European or American? A re-examination of the transatlantic influence over the IMF}}
date: last-modified
author: Dianyi Yang
format:
  beamer:
    theme: Madrid
bibliography: references.bib
csl: extra/apa.csl
project:
  execute-dir: "D:/OneDrive - London School of Economics/Desktop/GV499/IMF"
---

>>>>

---
title: European or American? A re-examination of the transatlantic influence over the IMF
# subtitle: GV499 Dissertation
header-includes: |
  \AtBeginDocument{\title[GV499 Dissertation]{European or American? A re-examination of the transatlantic influence over the IMF}}
date: last-modified
author: Dianyi Yang
format:
  beamer:
    theme: Madrid
bibliography: references.bib
csl: extra/apa.csl
---
